%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  THIS TEX FILE IS TO GENERATE PDF FILE FOR 
%%% 
%%%  COPYRIGHT (C) JIMMY LIN, 2013, UT AUSTIN
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[10pt]{beamer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  PACKAGES USED IN THIS TEX SOURCE FILE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{geometry}
\usepackage{color}
\usepackage{JSPPT}
\usepackage[style=ieee]{biblatex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% PRESENTATION INFORMATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Project Talk: Multiagent Behaviors in Neural Network}
\author[Jimmy Lin and Barry Feigenbaum]{\bf Jimmy Lin \\Barry Feigenbaum}
\institute{\bf Prof. Risto Miikkulainen\\[0.3cm] Department of Computer Science \\The University of Texas At Austin}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% TITLE PAGE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{large}
    \frame{\maketitle}%\titlepage
\end{large}

\frame{
    \frametitle{Table of Contents}
    \tableofcontents
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% DOCUMENTATION STARTS FROM HERE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Overview of Multiagent System}
\setbeamertemplate{itemize item}[ball]
\setbeamertemplate{itemize subitem}{$\int$}
% recapture contents of previous topic talks
\frame{
    \frametitle{Motivation}
   
}
% introduce multiagent behavior
\frame{
    \frametitle{Introduction}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% REFERENCES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\section{Appendix}
\frame[allowframebreaks]{
    \frametitle{References}
    \begin{thebibliography}{9}
    	\bibitem{bryant03} Bobby D. Bryant and Risto Miikkulainen (2003). Neuroevolution for Adaptive Teams. {\it Proceedings of the 2003 Congress on Evolutionary Computation} 1:2194-2201. 
    
        \bibitem{tan1993multi} Tan, Ming. "Multi-agent reinforcement learning:
        Independent vs. cooperative agents." {\it Proceedings of the Tenth
            International Conference on Machine Learning}. Vol. 337. 1993.
        
        \bibitem{rawar} Rawal, A.; Rajagopalan, P.; Miikkulainen, R., "Constructing competitive and cooperative agent behavior using coevolution," {\it Computational Intelligence and Games (CIG), 2010 IEEE Symposium on}, vol., no., pp.107,114, 18-21 Aug. 2010
        
        \bibitem{rajagopalan11} Rajagopalan, P.; Rawal, A.; Miikkulainen, R.; Wiseman, M.A.; Holekamp, K.E., "The role of reward structure, coordination mechanism and net return in the evolution of cooperation," {\it Computational Intelligence and Games (CIG), 2011 IEEE Conference on}, vol., no., pp.258,265, Aug. 31 2011-Sept. 3 2011
        
    	\bibitem{risto12} Risto Miikkulainen and Eliana Feasley and Leif Johnson and Igor Karpov and Padmini Rajagopalan and Aditya Rawal and Wesley Tansey (2012). {\it Multiagent Learning through Neuroevolution. Advances in Computational Intelligence} LNCS 7311:24-46.     
        
        \bibitem{yang02} Yanli Yang; Polycarpou, M.M.; Minai, A.A., "Opportunistically cooperative neural learning in mobile agents," {\it Neural Networks, 2002. IJCNN '02. Proceedings of the 2002 International Joint Conference on}, vol.3, no., pp.2638,2643, 2002
        
        \bibitem{yong09} Yong, C.H.; Miikkulainen, R., "Coevolution of Role-Based Cooperation in Multiagent Systems," {\it Autonomous Mental Development, IEEE Transactions on}, vol.1, no.3, pp.170,186, Oct. 2009
    \end{thebibliography}
}

\frame{
    \frametitle{Acknowledgement}
    Thanks.
}
\end{document}
